A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-01 paper.tex
Added an explicit proof of solveUnbounded to section 3.3

>>>>

Correctness of $\textsc{solveUnbounded}$ follows from these invariants. The
must-invariant guarantees that the environment can force the game into an error
state from $B^M$, therefore checking whether the initial state is in $B^M$ (as
in line~5) is sufficient to return \texttt{unrealisable}. The may-invariant
tells us that if $B^m[i] \equiv B^m[i+1]$ (line~6) then $Upre(B^m[i+1])
\subseteq B^m[i+1]$, i.e. there is a fixed point in the uncontrollable
predecessor. This guarantees that the controller can force the game to stay
within $B^m[i+1]$ and avoid error states indefinitely.
